Supporting Information

### 2016-08-23 portfolio/text/supp.Rnw
Typos

The basic model is a heirarchical linear regression with Gaussian errors
predicting $\log$ revenue, $\log(R_{i,t})$, for
each fisher $i$ and time (year) $t$:

@@

Whereas a typical heirarchical linear regression model
would estimate a single residual error scale term, $\sigma$,
we model the scale of the residual error  with
another heirarchical model with a similar form:

@@

The $\gamma$'s are estimated coefficients, three of which
are allowed to vary by strategy, constrained by normal distributions
and with estimated means:

>>>>

The basic model is a hierarchical linear regression with Gaussian errors
predicting $\log$ revenue, $\log(R_{i,t})$, for
each fisher $i$ and time (year) $t$:

@@

Whereas a typical hierarchical linear regression model
would estimate a single residual error scale term, $\sigma$,
we model the scale of the residual error  with
another hierarchical model with a similar form:

@@

The $\gamma$'s are estimated coefficients, three of which
are allowed to vary by strategy, constrained by normal distributions:
